ms_2_results

### 2017-09-15 man/ms_2_results.Rmd
update ms r

Vegetation greenness of *Quercus pyrenaica* forests were lower during the 2005 and 2012 year than the greenness observed for the reference period (Fig 1a EVI profile comparison), particu

>>>>

Vegetation greenness of *Quercus pyrenaica* forests were lower during the 2005 and 2012 year than the greenness observed for the reference period (:red_circle: Fig 1a EVI profile comparison), particu
